Ensuring Fairness with Transparent Auditing of Quantitative Bias in AI Systems

### 2024-08-17 slides/2024_8_30.tex
Added code snippets

\usepackage{CJKutf8}
\usepackage{datetime}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{xcolor}
\usepackage{ulem}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{url}
\usepackage{placeins}

@@

@@

@@

\begin{frame}
    \frametitle{Conclusion}
    \begin{itemize}
        \item Decision making by AI may be biased.
        \item With our framework tool, auditors can comprehensively
        review the fairness of an AI system.
    \end{itemize}
\end{frame}

>>>>

\usepackage{CJKutf8}
\usepackage{datetime}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{minted}
\usepackage{xcolor}
\usepackage{ulem}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{url}
\usepackage{placeins}

@@

\begin{frame}[fragile]
    \frametitle{Definition}
    \begin{align*}
        \text{equal\_opportunity} (\epsilon, \priv, \pos, \tru)
    \end{align*}

    This is implemented in our tool as a Python function:

    \begin{center}
    \begin{minipage}{0.8\textwidth}
    \begin{minted}[fontsize=\small, frame=single, linenos]{python}
def equal_opportunity(
    ratio,
    privileged_predicate,
    positive_predicate,
    truth_predicate):
    ...
    \end{minted}
    \end{minipage}
    \end{center}
\end{frame}

@@

\begin{frame}[fragile]
    \frametitle{Application}
    \begin{align*}
        \priv(r_i) & := r_i(\text{``race''}) \neq \text{``African-American''}\\
        \pos(r_i)  & := r_i(\text{``score\_text''}) \in \set{\text{``Medium''},\text{``High''}}\\
        \tru(r_i)  & := r_i(\text{``two\_year\_recid''}) == \text{True}
    \end{align*}
    These predicates can then be encoded with Python functions:
    \begin{center}
    \begin{minipage}{0.8\textwidth}
    \begin{minted}[fontsize=\small, frame=single, linenos]{python}
equal_opportunity(
    0.2,
    lambda row: row['race'] == 'African-American',
    lambda row: row['score_text']
      in {'Medium', 'High'},
    lambda row: row['is_recid'] == '1')
    \end{minted}
    \end{minipage}
    \end{center}
\end{frame}

@@

\begin{frame}
    \frametitle{Conclusion}
    \begin{itemize}
        \item Decision making by AI may be biased.
        \item With our framework tool, auditors can comprehensively
        review the fairness of an AI system.
    \end{itemize}

    This slides is available at \url{https://github.com/RexYuan/Shu}.
\end{frame}
